---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  asciicast_knitr_output = "html"
)
asciicast::init_knitr_engine(
  echo = TRUE,
  echo_input = FALSE,
  startup = quote({
    library(lgbthue)
    options(
      cli.num_colors = cli::truecolor,
      asciicast_theme = list(background = c(255, 255, 255))
    )
  })
)
library(lgbthue)
options(lgbthue_font_size = 1.7)
set.seed(123L)
```

# lgbthue

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/lgbthue)](https://CRAN.R-project.org/package=lgbthue)
[![R-CMD-check](https://github.com/turtletopia/lgbthue/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/turtletopia/lgbthue/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/turtletopia/lgbthue/graph/badge.svg)](https://app.codecov.io/gh/turtletopia/lgbthue)
<!-- badges: end -->

The goal of lgbthue is to provide palette data for pride flags for use by [gglgbtq](https://github.com/turtletopia/gglgbtq) and future projects.

## Installation

You can install the development version of lgbthue from [GitHub](https://github.com/) with:

```{r install, eval = FALSE}
# install.packages("pak")
pak::pak("turtletopia/lgbthue")
```

## User guide

To list all available palettes, call `show_pride()`. The output would be very long, however, so I'm not including the result. Instead, know it is possible to filter by tags and palette sizes:

```{asciicast pride_filtered}
show_pride(tags = "rainbow", sizes = c(6, 8))
```

Accessing one of these is best done by `palette_lgbtq()`:

```{asciicast palette_lgbtq}
palette_lgbtq("lesbian")
```

Such palettes can be used anywhere a palette is needed, plots in particular. For example:

```{r plot}
group <- rep(1:6, each = 10)
x <- group + .5 * rnorm(60)
y <- runif(60, 1, 1.5) * sqrt(group)
plot(x, y, pch = 19, col = palette_lgbtq("rainbow")[group], cex = 2)
```

If you wish to use these palettes with ggplot2, [gglgbtq](https://github.com/turtletopia/gglgbtq) adapts these palettes to that particular use case.

Moreover, as a palette draws from the colors of a flag, a `seq()` method is provided that transforms a palette into a sequence so that e.g. a vertical bar with correct flag colors can be shown:

```{asciicast seq}
seq(palette_lgbtq("trans"))
```

## Gallery

Only a few most common palettes are included below. For the complete list, see [palette gallery vignette](https://turtletopia.github.io/lgbthue/articles/gallery.html).

```{r palettes, fig.height=1.6}
plot(palette_lgbtq("rainbow"))
plot(palette_lgbtq("philadelphia"))
plot(palette_lgbtq("progress"))
plot(palette_lgbtq("lesbian"))
# In its original meaning of "gay men"
plot(palette_lgbtq("gay"))
plot(palette_lgbtq("bisexual"))
# Background added to avoid the "disappearance" of the white stripe
plot(palette_lgbtq("transgender"), background = "gray92")
plot(palette_lgbtq("asexual"))
plot(palette_lgbtq("nonbinary"))
plot(palette_lgbtq("intersex"))
```
